Data Preparation

### 2019-03-14 Data Preparation.Rmd
add an issue with d_transcript
create df tailored to pillar 1

@@

# Save Data
```{r}
save(
  d_course, list_AoD_assessment, d_AoD, d_assessment, d_ILO,
  file = "Output/data_general.RDATA"
  )

save(d_transcript, file = "Output/data_pillar_1.RDATA")

>>>>

  # SSC2046, a course I took, but excluded from my transcript is absent from the data set
  filter(`Student ID` == "6087587") %>%
  arrange(`Course ID`) %>%
  pull(`Course ID`)

@@

## df tailored to pillar 1
```{r}
d_transcript_augmented <- d_transcript %>%  left_join(select(d_course, - Period), by = c("Course ID"))

d_transcript_informative <- d_transcript_augmented %>%

  # Exclude courses taken by majority of students (uninformative)
  filter(
    Type != "Mandatory",
    ! Letters %in% c("SKI", "PRO", "SAS", "SAH", "SAC")
    ) %>%

  select(`Student ID`, `Course ID`, time, grade_ceil)
```

# Save Data
```{r}
save(d_course, list_AoD_assessment, d_AoD, d_assessment, d_ILO, file = "Output/data_general.RDATA")

save(d_transcript_augmented, d_transcript_informative, file = "Output/data_pillar_1.RDATA")
